```{r}
library(ggplot2)
library(dplyr)
library(tidyr)

library(ggeasy)
```

a) Create a diverging stacked bar chart to display the data. 
```{r, fig.height=10, fig.width=16}
data(mtcars)

head(mtcars)
```

```{R}
mtcars$am <- factor(mtcars$am, labels = c("Automatic", "Manual"))

ggplot(mtcars, aes(x = mpg, fill = am)) +
    geom_density(alpha = 0.5) +
    labs(title = "Distribution of Fuel Efficiency by Transmission Type",
         x = "mpg",
         fill = "Transmission Type") +
    theme_minimal()
```



Legend Operations:

a) easy_move_legend() -> theme(legend.position = "bottom")
b) *easy_rotate_legend() -> guides(fill = guide_legend(ncol = 1))*
c) easy_remove_legend_title -> theme(legend.title = element_blank())
d) easy_remove_legend -> theme(legend.position = "none")

```{R}
ggplot(mtcars, aes(x = mpg, fill = am)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of Fuel Efficiency by Transmission Type",
       x = "mpg",
       fill = "Transmission Type") +
  theme_minimal()+
  theme(legend.position = "bottom")
```



Change text size:

a) easy_x_axis_labels_size(20) -> theme(axis.text.x = element_text(size = 20))
b) easy_plot_title_size(20) -> theme(plot.title = element_text(size = 20))
c) easy_legend_size(20) -> theme(legend.title = element_text(size = 20))
d) easy_legend_text_size(20) -> theme(legend.text = element_text(size = 20))
e) easy_title_bold() -> theme(plot.title = element_text(face = "bold"))

```{R}
ggplot(mtcars, aes(x = mpg, fill = am)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of Fuel Efficiency by Transmission Type",
       x = "mpg",
       fill = "Transmission Type") +
  theme_minimal()
```



Rotate labels:

a) *easy_rotate_labels()* -> 
  theme(
      axis.text.x = element_text(angle = 90),
      axis.text.y = element_text(angle = 90)
  )

```{R}
ggplot(mtcars, aes(x = mpg, fill = am)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of Fuel Efficiency by Transmission Type",
       x = "mpg",
       fill = "Transmission Type") +
  theme_minimal()
```



Remove axis/gridlines:

a) easy_remove_x_axis() ->
  theme(
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank()
  )
b) easy_remove_x_axis(what = "ticks")
c) easy_remove_gridlines() ->
  theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank()
  )

```{R}
ggplot(mtcars, aes(x = mpg, fill = am)) +
  geom_density(alpha = 0.5) +
  labs(title = "Distribution of Fuel Efficiency by Transmission Type",
       x = "mpg",
       fill = "Transmission Type") +
  theme_minimal()
```
